---
params: 
  title: ""
  abstract: ""
  doi: ""
  datadir: ""
title: "`r params$title`"
output: 
  html_document:
    theme: flatly
    highlight: zenburn
    toc: true
    code_folding: "hide"
    includes:
      before_body: header.html
      after_body: footer.html
    # toc_float: true
---

<style type="text/css">
div.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}

h1, .h1, {
    margin-top: 84px;
}

</style>

```{r load_libs, echo=FALSE, message=FALSE, warning=FALSE}

datadir <- params$datadir

library(devtools)
library(anytime)

# devtools::install_github("pablobarbera/twitter_ideology/pkg/tweetscores")
# devtools::install_github("geoffjentry/twitteR")
# devtools::install_github("mkearney/rtweet")
# devtools::install_github("ropensci/rAltmetric")

library(tidyverse)

# API stuff
library(rAltmetric)
library(rvest)
library(crevents)

# Analysis
library(umap)
library(dbscan)
library(tidytext)
library(topicmodels)
library(ldatuning)
library(tm)
library(qlcMatrix)

# plotting stuff
library(ggrepel)
library(ggridges)
library(RColorBrewer)
library(htmlwidgets)
library(plotly)
library(ggdendro)
library(dendextend)
```

# Paper Abstract

```{r, results="asis", echo=FALSE}
tg <- function (link, text){
  paste0("<a href='", link, "'>", text, "</a>")
}

cat(tg(paste0("https://dx.doi.org/", doi[2]), "View paper on journal site"))
cat("<br>")
cat(tg(article_full_url, "View paper on Altmetric"))
cat("<br>")
```

`r params$abstract`

# LDA topic modeling analysis {.tabset .tabset-fade .tabset-pills}

One of the challenges in altmetrics audience analysis is detailed classification of the various groups of users who are interested in a paper on social media. This is due to the limited information available about each user—Twitter limits user biographies to 160 characters.

Our approach is to understand user characteristics not by looking at the information supplied by each user, but the information supplied by that user's followers.

Each user that tweets about an article exposes the article to their own unique audience of followers. Under the principle of network homophily, we expect that each user shares similar characteristics to the users within their network, e.g., biologists tend to be followed by biologists and other users interested in biology.

## Code

### Scrape tweets referencing paper

The code below will first query the Crossref Event Data API to get a list of tweets/RTs referencing the specified article. Only the status IDs (not full tweets) are stored in Crossref, so we rehydrate the full text of the tweets using the Twitter API.

In some cases, Crossref may be missing many of the tweets documented on Altmetric for the same paper. When this happens, the code below will fall back to scraping handles and tweet IDs from the corresponding Altmetric page.

```{r scrape_ref_tweets, warning=FALSE, message=FALSE, error=FALSE}

# query and clean event data gathered from Crossref API
events <- crev_query(obj_id=params$doi, source="twitter")$message$events %>%
  dplyr::select(names=subj.author.url, timestamps=timestamp, status = subj_id) %>%
  mutate(names=gsub("http://www.twitter.com/", "", names),
         status=gsub("http://twitter.com/.*statuses/", "", status)) %>%
  mutate(names=gsub("twitter://user\\?screen_name=", "", names),
         status=gsub("twitter://status\\?id=", "", status))

# get user metadata
handles <- unique(events$names)

# For papers where Crossref is missing >50% of tweets, fall back to
# scraping from Altmetric
if(length(handles)/as.numeric(article_df$cited_by_tweeters_count) < 0.5){
  
  summary_page <- read_html(article_full_url)
  twitter_url <- paste0(article_full_url, "/twitter")
  twitter_page <- read_html(twitter_url)
  
  # number of pages is the ceiling of total tweets/100
  totals <- twitter_page %>% html_nodes("div.text strong") %>% html_text()
  npages <- ceiling(as.integer(totals[1])/100)
  
  # loop through pages of tweets on altmetric to get handles of tweeting users
  events <- data.frame()
  for(page in 1:npages){
    # url <- paste0(article_base_url, id, "/twitter/page:", page)
    page_url <- paste0(twitter_url, "/page:", page)
    page <- read_html(page_url)
    
    names <- gsub("@", "", html_nodes(page, "div.handle") %>% html_text())

    status <- gsub(".*tweet_id=", "", html_nodes(page, "a.favorite") %>% 
                     html_attr("href"))

    timestamps <- html_nodes(page, "time") %>% html_attrs() %>% unlist()
    
    events <- bind_rows(events, data.frame(names, timestamps, status))
  }
  
  handles <- unique(events$names)
}

# get user metadata from Twitter API
user_data <- lookup_users(handles)
  
tweets <- lookup_tweets(events$status) %>%
  dplyr::select(names=screen_name, 
                tweets=text, 
                retweet_screen_name, 
                status=status_id)

events <- events %>%
  left_join(tweets)

# separate data by original tweets and RTs
original <- events %>% 
  dplyr::filter(is.na(retweet_screen_name)) %>% 
  group_by(names, tweets) %>% 
  count %>% 
  arrange(desc(n))

rts <- events %>% 
  dplyr::filter(!is.na(retweet_screen_name)) %>% 
  group_by(retweet_screen_name, tweets) %>% 
  count %>% 
  arrange(desc(n))

```

### Scrape follower lists

For each unique user that has (re-)tweeted the article, we then collect the handles of their followers using the Twitter API.

Due to API restrictions this can be very time-consuming, so a .rds file containing these data will be stored to disk enabling analyses to be repeated without needing to re-scrape the data.

```{r scrape_follower_ids, warning=FALSE, message=FALSE, error=FALSE}
#-----------------------------------------------------------------------------
# Get follower lists for users
# due to Twitter API limits, this will take at least N minutes, 
# where N is the number of unique users that have tweeted about an article
#
# users with >5,000 followers will require multiple API calls to scrape their
# full follower lists, so a user with 75,000 followers will take 
# the same amount of time to process as 15 users with <5,000 followers each 
# (~15 minutes)
#-----------------------------------------------------------------------------

# altmetric_data_full_fh <- paste0(datadir, "altmetric_data_full.rds")
altmetric_data_full_fh <- paste0(datadir, "/article_data/altmetric_data_full_", article_id, ".rds")

if(file.exists(altmetric_data_full_fh)){
  altmetric_data_full <- readRDS(altmetric_data_full_fh)
} else {

  # get follower metadata from Twitter API
  # sleep interval--if more than 15 API calls will be required, use one call per minute to 
  # minimize weird timeout issues
  fc_mod <- ceiling(user_data$followers_count/5000)
  sleep <- ifelse(sum(fc_mod)>15, 60, 0)
  reset <- TRUE
  
  if(!exists("altmetric_data_full") | reset){
    altmetric_data_full <- tibble(account=character(), followers=list())
  }
  for(user in (nrow(altmetric_data_full)+1):nrow(user_data)){
    
    # refresh OAuth handshake
    # if(user %% 20 == 0){
    #   twitteR::setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
    # }
    
    if(user_data[user,]$protected){
      cat(paste0("User ", user_data[user,]$screen_name, " is protected--skipping\n"))
    } else {
      # cat(paste0("Getting follower list for: ", user_data[user,]$screen_name, 
      #  " (", user, " of ", nrow(user_data), ")...\n"))
    
      altmetric_data_user <- user_data[user,] %>%
        dplyr::select(account=screen_name) %>% #head
        mutate(followers = getFollowers(screen_name=account, oauth=my_oauth, sleep=sleep) %>% 
                 data.frame %>% 
                 as.list)
        
      altmetric_data_full <- bind_rows(list(altmetric_data_full, altmetric_data_user))
    }
  }
  
  saveRDS(altmetric_data_full, altmetric_data_full_fh)
}
```

### Scrape follower bios

Next, we scrape the bios of the followers (limited to the 10,000 most recent followers) for each account that has (re-)tweeted the article and compile these bios into a single "document" per account.

Due to API restrictions this can be very time-consuming, so a .rds file containing these data will be stored to disk enabling analyses to be repeated without needing to re-scrape the data.

```{r scrape_follower_bios, warning=FALSE, message=FALSE, error=FALSE}

altmetric_follower_fh <- paste0(datadir, "/article_data/follower_bios_", article_id, ".rds")

reset <- TRUE

if(file.exists(altmetric_follower_fh)){
  out_df <- readRDS(altmetric_follower_fh)
} else {
  
  if(!exists("out_df") | reset){
    out_df <- data.frame(account=character(), bios=character())
  }

  for(i in (length(unique(out_df$account))+1):nrow(altmetric_data_full)){

    # cat(paste0("Getting follower bios for: ", altmetric_data_full[i,]$account, 
    #        " (", i, " of ", nrow(altmetric_data_full), ")...\n"))
        
    if(length(unlist(altmetric_data_full[i,]$followers)) > 0){
      bios <- try(get_follower_bios(followers=altmetric_data_full[i,]$followers))
  
      if(!inherits(bios, "try-error")){
        acct_follower_bios <- data.frame(account=altmetric_data_full[i,]$account, bios)
    
        out_df <- bind_rows(list(out_df, acct_follower_bios))  
      } else {
        # cat(paste0("Encountered error for user--results will not be included\n"))
      }
    
      Sys.sleep(10)
    }

  }
  
  saveRDS(out_df, altmetric_follower_fh)
}
```

### Prepare data for LDA model

We calculate the frequencies of every term that occurs 10 or more times in each document, excluding common stop words. Note that because emoji and hashtags are commonly used to convey semantic meaning in a user's bio, we include these as unique "words". From the word frequency data, we then generate a document term matrix, which serves as the input for the LDA model.

```{r clean_follower_bios, warning=FALSE, message=FALSE, error=FALSE}
# convert emoji and hashtags to text, collapse follower bios
bios <- out_df %>%
  dplyr::filter(account_lang=="en") %>%
  dplyr::select(account, bio=description, name) %>%
  # mutate(bio=ifelse(nchar(bio)!=0, bio, "missingbio")) %>%
  # unite(description, c(name, bio), sep=" ") %>%
  mutate(description= paste0(name, " ", bio)) %>%
  mutate(description = emoji_to_text(description)) %>%
  mutate(description = gsub("-", "", description)) %>%
  mutate(description = gsub("#", "hashtag", description)) %>%
  group_by(account) %>%
  summarise(doc=paste(description, collapse = " ")) %>%
  mutate(doc=iconv(doc, 'utf-8', 'ascii', sub=''))

# define stopwords
custom_stopwords <- c("https", "http", "t.co", "gmail.com", "views", "love", "lover", "tweets",
                      "rts", "follow", "twitter", "endorsement", "fan", "james", "michael",
                      "andrew", "ryan", "chris", "matt", "och", "rt", "opinions", "paul",
                      "endorsements", "account", "life", "john", "david", "social", "retweets",
                      stopwords(kind="en"), stopwords(kind="danish"), stopwords(kind="dutch"), 
                      stopwords(kind="finnish"), stopwords(kind="french"), stopwords(kind="german"),
                      stopwords(kind="hungarian"), stopwords(kind="italian"), stopwords(kind="norwegian"),
                      stopwords(kind="portuguese"), stopwords(kind="russian"), stopwords(kind="spanish"),
                      stopwords(kind="swedish"))

# tokenize, dropping stopwords
bios_tokenized <- bios %>%
  unnest_tokens(word, doc) %>%
  dplyr::filter(!(word %in% custom_stopwords))

rm(bios)

# apply default stopword list and count frequencies
word_counts <- bios_tokenized %>%
  anti_join(stop_words) %>%
  count(account, word, sort = TRUE) %>%
  dplyr::filter(n>=10)

rm(bios_tokenized)

gc()

#-----------------------------------------------------------------------------
# TESTING use 2-word tokens?
#-----------------------------------------------------------------------------
# bios_tokenized2 <- bios %>%
#   unnest_tokens(ngram, doc, token = "ngrams", n = 2) %>%
#   dplyr::filter(!(grepl(paste(custom_stopwords, collapse="|"), ngram)))
# 
# ngram_counts <- bios_tokenized2 %>%
#   count(account, ngram, sort = TRUE) %>%
#   dplyr::filter(n>=5) %>%
#   separate(ngram, c("word", "word2"), sep = " ") %>%
#   anti_join(stop_words) %>%
#   dplyr::rename(word1=word, word=word2) %>%
#   anti_join(stop_words) %>%
#   unite(word, c("word1", "word"), sep=" ")

#-----------------------------------------------------------------------------
# run over entire dataset
#-----------------------------------------------------------------------------
bios_dtm <- word_counts %>%
  cast_dtm(account, word, n)

# 2-word tokens only
# bios_dtm <- ngram_counts %>%
#   cast_dtm(account, word, n)

# single words + 2-word tokens
# bios_dtm <- bind_rows(word_counts, ngram_counts) %>%
#   cast_dtm(account, word, n)

```

### Run LDA model

This code runs the Latent Dirichlet Allocation (LDA) model to represent the corpus of documents as a mixture of K "topics." Each topic is represented by a different set of words/terms that frequently co-occur. The gamma values are interpreted as the fraction of each document corresponding to each of the K topics. 

```{r run_lda, warning=FALSE, message=FALSE, error=FALSE}

bios_lda6 <- LDA(bios_dtm, k = 12, control = list(alpha=0.1, seed = 5678), method="VEM")
bios_lda_td <- tidy(bios_lda6)

top_terms <- bios_lda_td %>%
  group_by(topic) %>%
  top_n(30, beta) %>%
  ungroup() %>%
  arrange(topic, -beta) %>% 
  mutate(term = text_to_emoji(term)) %>%
  mutate(term = gsub("hashtag", "#", term))

topics_terms <- top_terms %>% 
  dplyr::select(-beta) %>% 
  # mutate(topic=paste0("t", topic)) %>%
  group_by(topic) %>% 
  summarise(top_10=paste(term, collapse=", ")) %>% 
  ungroup()

bios_lda_gamma <- tidy(bios_lda6, matrix = "gamma") %>%
  rowwise() %>%
  mutate(gamma=gamma+runif(1,0,0.0001))

docs_order <- bios_lda_gamma %>%
  group_by(document) %>%
  arrange(topic, -gamma) %>%
  top_n(1, gamma) %>%
  rename(topic_group = topic) %>%
  dplyr::select(-gamma)

```

## Results

### Plot topic breakdown by user

This plot shows the topic breakdowns of each account according to the frequencies of each of the K topics expressed in the bios of their followers.

```{r plot_topic_structure, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}

cols <- c(brewer.pal(9, "Set1"), brewer.pal(9, "Set3"))

p <- bios_lda_gamma %>%
  mutate(document=factor(document, levels=docs_order$document)) %>%
  left_join(topics_terms, by="topic") %>%
  mutate(topic=paste0(topic, ": ", top_10)) %>%
  mutate(topic=factor(topic, levels=unique(topic))) %>%
  ggplot(aes(x=document, y=gamma, fill=topic))+
  geom_bar(stat="identity", position="stack")+
  scale_fill_manual(values=cols)+
  scale_y_continuous(expand = c(0,0))+
  scale_x_discrete(position = "top")+ 
  xlab("Account")+
  theme(legend.position="bottom",
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  guides(fill=guide_legend(ncol=1))

p2 <- ggplotly(p) %>%
  layout(legend = list(orientation = "v",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     yanchor = "bottom",
                     x = 0, y=-1))

wrapper <- function(x, ...) paste(strwrap(x, ...), collapse = "\n")
p_thumb <- p+
  ggplot2::annotate("text", x=0, y=0.5, hjust=0, label=wrapper(article_df$title, width = 30), size=6)+
  theme(legend.position="none", axis.ticks.x=element_blank(), axis.title.x=element_blank())

ggsave(paste0(datadir, "/output/figures/", gsub(".html", ".png", nb_file)), 
       plot=p_thumb, width = 4, height=2, dpi=125)

htmlwidgets::saveWidget(p2, 
                        file=paste0(datadir, "/figs/topic_breakdown_by_user_", article_id, ".html"),
                        title=paste0("topic_breakdown_by_user_", article_id))

p2

```

# Network homophily analysis {.tabset .tabset-fade .tabset-pills}

Many of the papers analyzed have a non-trivial fraction of users whose inferred audience topics are strongly suggestive of affiliation with white nationalism and other right-wing ideologies. According to the principle of network homophily, we would expect these users' followers to substantially overlap the follower bases of prominent white nationalists. 

These results show that most papers exhibit a continuous gradient between their affiliation with academic communities and their affiliation with white nationalist communities. Some users have up to 40% of their followers who also follow prominent white nationalist accounts and <1% who follow prominent scientist accounts, corresponding to a ~100-fold enrichment of white nationalists among their follower base.

## Code

Using a curated a set of 20 white nationalist accounts and 20 scientist accounts, we calculated the network homophily between each of these 40 accounts and each of the N users that have tweeted the paper, producing an Nx40 similarity matrix. We then applied PCA+UMAP to this matrix to reduce the dimensionality to Nx2.

### Generate similarity matrix

```{r homophily_umap, warning=FALSE, message=FALSE, error=FALSE}
#-----------------------------------------------------------------------------
# Generate follower overlap matrix: 
# 1 row per test account, i, 1 column per reference account, j
# each cell contains fraction of i's followers that also follow j
#-----------------------------------------------------------------------------
sim_matrix <- altmetric_data_full %>%
  dplyr::filter(length(followers)>=10) %>%
  group_by(account) %>%
  nest() %>% 
  mutate(test=map(data, ~match_followers(.$followers))) %>% unnest(test)

saveRDS(sim_matrix, paste0(datadir, "/article_data/sim_matrix_", article_id, ".rds"))

# apply PCA to count matrix
sim_matrix_pca <- sim_matrix %>%
  dplyr::select(-data) %>%
  mutate(sum = rowSums(.[2:41])) %>% 
  dplyr::filter(sum!=0) %>%
  dplyr::select(-sum) %>%
  nest() %>%
  mutate(pca = purrr::map(data, ~prcomp(.x %>% dplyr::select(-account), center = TRUE, scale = TRUE)), 
         pca_tidy = purrr::map2(pca, data, ~broom::augment(.x, data = .y)))

# apply UMAP to PCA data
sim_matrix_umap <- sim_matrix_pca[[3]][[1]] %>% 
  dplyr::select(.fittedPC1:.fittedPC40) %>%
  data.frame() %>%
  umap(n_neighbors=30, random_state=36262643)

```

## Results

### Plot UMAP homophily embedding

This plot shows the 2D embedding of accounts according to their homophily with the two reference groups. We typically see a gradient from strong scientist homophily (blue) to strong white nationalist homophily (red), but the extent of these differences can vary. A paper that is exposed primarily to academic audiences will have mostly blue points, papers exposed to white nationalist audiences will have more red points.

```{r homophily_umap_plot, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}

umap_plotdat <- bind_cols(sim_matrix_pca[[3]][[1]], data.frame(sim_matrix_umap$layout)) %>%
  left_join(user_data %>% dplyr::rename(account=screen_name),
            by="account") %>%
  mutate(wn_mean=rowMeans(dplyr::select(.,vdare:NewRightAmerica), na.rm = TRUE),
         sc_mean=rowMeans(dplyr::select(.,pastramimachine:girlscientist), na.rm = TRUE)) %>%
  mutate(affiliation=log10(wn_mean/(sc_mean+0.001))) %>%
  dplyr::filter(sc_mean != 0 & wn_mean != 0) %>%
  mutate(urls=paste0("https://twitter.com/", account))

# plotdat2 <- plotdat
hdb_clust <- umap_plotdat %>%
  dplyr::select(X1:X2) %>%
  as.matrix() %>%
  hdbscan(x=., minPts=10)

umap_plotdat$cluster <- as.character(hdb_clust$cluster)

lda_gammas <- bios_lda_gamma %>%
  mutate(document=factor(document, levels=docs_order$document)) %>%
  left_join(topics_terms, by="topic") %>%
  mutate(topic=paste0(topic, ": ", top_10)) %>%
  mutate(topic=factor(topic, levels=unique(topic))) %>%
  group_by(document) %>%
  arrange(topic, -gamma) %>%
  top_n(1, gamma) %>%
  rename(account=document)

plot_embedding <- function(plotdat){
  
  p <- plotdat %>% # merge with user_data to get followers_count + other info
    ggplot(aes(x=X1, y=X2, label=account, colour=affiliation))+
    geom_point(aes(size=log(followers_count)), alpha=0.8)+
    scale_colour_gradientn("WN:Scientist Follower Ratio", 
                           colors=rev(brewer.pal(9, "RdBu")), 
                           breaks=seq(-3,3),
                           labels=c("1:1000", "1:100", "1:10","1:1","10:1","100:1","1000:1"),
                           limits=c(-3,3))+
    theme_dark()+
    theme(legend.position="bottom")
  
  ply <- ggplotly(p)
  
  # Clickable points link to profile URL using onRender: https://stackoverflow.com/questions/51681079
  ply$x$data[[1]]$customdata <- plotdat$urls
  #pp  <- add_markers(pp, customdata = ~url)
  plyout <- onRender(ply, "
                     function(el, x) {
                     el.on('plotly_click', function(d) {
                     var url = d.points[0].customdata;
                     //url
                     window.open(url);
                     });
                     }
                     ")

  plyout
}

htmlwidgets::saveWidget(plot_embedding(umap_plotdat), 
                        file=paste0(datadir, "/figs/homophily_ratio_", article_id, ".html"),
                        title=paste0("homophily_ratio_", article_id))

plot_embedding(umap_plotdat)

```

# Cosine similarity analysis {.tabset .tabset-fade .tabset-pills}

As a sanity-check for the LDA model, we can also examine how users cluster in other ways. Here we calculate the cosine similarity between the follower bios of each pair of users and apply hierarchical clustering and PCA+UMAP to explore these relationships.

## Code

This code uses the document term matrix to calculate a distance matrix between each pair of users, where the M_i,j entry indicates the cosine similarity score (ranging from 0-1) between the follower bios of user i and user j.

```{r dtm_cosine, error=FALSE, message=FALSE, warning=FALSE}
m <- as.matrix(bios_dtm)
# distMatrix <- dist(m, method="euclidean")

sim <- m / sqrt(rowSums(m * m))
sim <- sim %*% t(sim)
distMatrix <- as.dist(1 - sim)

rm(m)
gc()
```

## Results

### Hierarchical clustering by cosine similarity

A typical way to visualize the patterns of "relatedness" among a sample is to perform agglomerative hierarchical clustering. The relatedness of this sample (i.e., similarity in content of follower bios) is displayed in the dendrogram below.

```{r hclust_cosine, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}
groups <- hclust(distMatrix,method="ward.D")
dend <- as.dendrogram(groups)
dend_data <- dendro_data(dend, type = "rectangle")
label_order <- dend_data$labels %>%
  dplyr::rename("account"="label")

# coldf <- data.frame(topic=c(1,10:12,2:9), col=cols[c(1,10:12,2:9)])
coldf <- data.frame(topic=c(1,10:12,2:9), col=cols[1:12])

lgo <- lda_gammas %>% 
  mutate(topic=as.numeric(gsub(":.*", "", topic))) %>% 
  left_join(coldf, by="topic") %>% 
  ungroup() %>% 
  left_join(label_order, by="account") %>% 
  arrange(x)

p_dend <- dend %>% 
   set("labels", "") %>%    # change labels
  # set("labels_col", lgo$col) %>% set("labels_cex", 1) %>%
  set("leaves_pch", 19) %>% set("leaves_cex", 1) %>% set("leaves_col", lgo$col) %>%
  plot

ggsave(paste0(datadir, "/figs/cosine_hclust_dend_", article_id, ".png"), 
       plot=p_dend, width = 12, height=12)
```

### UMAP embedding by cosine similarity

This is analogous to performing PCA on SNPs within a population—it tells us how closely "related" different groups of users are, according to pairwise similarity between their followers' bios. 

```{r umap_cosine, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}
dmp <- prcomp(as.matrix(distMatrix), center=TRUE, scale=TRUE)

dmp_df <- dmp$x %>%
  as_tibble(rownames="account") %>%
  inner_join(lda_gammas, by="account")

dmp_umap <- dmp$x %>% as.data.frame() %>%
    umap(n_neighbors=20, random_state=36262643)

dmp_df2 <- dmp_umap$layout %>%
  as_tibble(rownames="account") %>%
  inner_join(lda_gammas, by="account") %>%
  left_join(umap_plotdat, by="account")

p2 <- dmp_df2 %>% 
  ggplot(aes(x=V1, y=V2, label=account, colour=topic))+
  geom_point(aes(size=wn_mean), alpha=0.7)+
  scale_colour_manual(values=cols)+
  theme_dark()+
  theme(legend.position="none")#+
  # guides(colour=guide_legend(ncol=1))

htmlwidgets::saveWidget(ggplotly(p2), 
                        file=paste0(datadir, "/figs/cosine_umap_", article_id, ".html"),
                        title=paste0("cosine_umap_", article_id))

ggplotly(p2)

# plot PCA
# p5 <- dmp_df %>%
#   # mutate(topic_num=gsub(":.*", "", topic)) %>%
#   ggplot(aes(x=PC1, y=PC2, colour=topic, label=account))+
#   geom_point()+
#   scale_colour_manual(values=cols)+
#   theme(legend.position="none")+
#   guides(colour=guide_legend(ncol=1))
# 
# p5_ply <- ggplotly(p5) %>%
#   layout(legend = list(orientation = "v",   # show entries horizontally
#                      xanchor = "center",  # use center of legend as anchor
#                      yanchor = "bottom",
#                      x = 0, y=-1))
# 
# htmlwidgets::saveWidget(p5_ply, 
#                         file=paste0(datadir, "/figs/cosine_pca_", article_id, ".html"),
#                         title=paste0("cosine_pca_", article_id))
# 
# p5_ply

```

# Missing data analysis {.tabset .tabset-fade .tabset-pills}

The LDA topic model described above is applied to the Twitter biographies of each user's followers. However, having a biography is not mandatory and many users opt to leave their bio blank. Here we explore if these patterns of missingness systematically differ among the topic groups.

## Code

The code below calculates the fraction of each user's followers that have empty bios.

```{r calc_missing, error=FALSE, warning=FALSE, message=FALSE}
bios_m <- out_df %>%
  # dplyr::filter(account_lang=="en") %>%
  dplyr::select(account, bio=description, name) %>%
  mutate(bio=ifelse(nchar(bio)!=0, 0, 1)) %>% 
  # unite(description, c(name, bio), sep=" ") %>%
  group_by(account) %>%
  summarise(tot=n(), nmissing=sum(bio), pct=nmissing/tot) %>% #dim
  # dplyr::rename("document"="account") %>%
  inner_join(lda_gammas, by="account") %>%
  inner_join(umap_plotdat, by="account")

rm(out_df)
gc()
```

## Results

### Plot missingness distributions by group

This plot shows the distribution of fraction of missing bios for each of the K topics.

```{r missing_data, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}


p4 <- bios_m %>%
  mutate(topic_num=gsub(":.*", "", topic)) %>%
  ggplot(aes(x=topic_num, y=pct, colour=topic, label=account))+
  geom_jitter(size=3, alpha=0.6)+
  geom_boxplot(outlier.shape=NA)+
  scale_colour_manual(values=cols)+
  theme(legend.position="bottom",
        axis.title.y=element_blank(),
        axis.text.x=element_blank())+
  guides(colour=guide_legend(ncol=1))

p4_ply <- ggplotly(p4) %>%
  layout(legend = list(orientation = "v",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     yanchor = "bottom",
                     x = 0, y=-1))

htmlwidgets::saveWidget(p4_ply, 
                        file=paste0(datadir, "/figs/missing_dist_", article_id, ".html"),
                        title=paste0("missing_dist_", article_id))

p4_ply

```

### Correlation between missing data and WN homophily

This plot investigates how patterns of missingness among follower bios are associated with patterns of white nationalist homophily described above. In many of the papers analyzed, we often see a positive correlation between proportion of followers with missing bios and homophily with prominent white nationalists, but only within a subset of topical groups inferred by the LDA model. This suggests that missingness within bios is itself a common feature of WN communities or WN-adjacent communities on Twitter. This also explains why some users have strong network homophily with known white nationalists, but do not show a strong topical association in the LDA model—essentially, the followers that drive WN network homophily are systematically contributing less information to the LDA model and skewing some users to look more like other topics.

```{r missing_data_homophily, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}
p4a <- bios_m %>%
  mutate(topic_num=gsub(":.*", "", topic)) %>%
  dplyr::filter(pct<0.5) %>%
  ggplot(aes(x=pct, y=wn_mean, group=topic_num, colour=topic, label=account))+
  geom_point()+
  geom_smooth(method="lm", se=F)+
  scale_colour_manual(values=cols)+
  # facet_wrap(~topic_num, scales="free")+
  xlab("Fraction of followers with missing bios")+
  ylab("WN Homophily")+
  theme(legend.position="bottom")+
  guides(colour=guide_legend(ncol=1))

p4a_ply <- ggplotly(p4a) %>%
  layout(legend = list(orientation = "v",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     yanchor = "bottom",
                     x = 0, y=-1))

htmlwidgets::saveWidget(p4a_ply, 
                        file=paste0(datadir, "/figs/missing_homophily_cor_", article_id, ".html"),
                        title=paste0("missing_homophily_cor_", article_id))

p4a_ply

```

# Retweet timeline analysis {.tabset .tabset-fade .tabset-pills}

One of the most difficult questions to address is how a paper's exposure originates in or is transmitted into particular networks. Here we attempt to trace a paper's path through these inferred networks by examining the history of retweets that reference the paper. Some tweets may only be retweeted by users within relatively tight networks, whereas others may have a much more diverse exposure.

## Code

## Results

### Timeline plot

```{r timeline, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}
# p_times <- ts_df %>% 
p_times <- events %>% 
  rename(account=names, rt=retweet_screen_name) %>% 
  left_join(dmp_df2, by="account") %>% 
  mutate(rt=ifelse(is.na(rt), account, rt)) %>%
  group_by(rt, tweets) %>% 
  arrange(timestamps) %>% 
  mutate(order=row_number(), n=n()) %>% 
  dplyr::filter(n>3) %>%
  ungroup() %>%
  ggplot(aes(x=timestamps, y=order, group=tweets, label=account))+
  geom_line(colour="grey80")+
  geom_point(aes(colour=topic, size=wn_mean), alpha=0.5)+
  scale_colour_manual(values=cols)+
  scale_y_log10()+
  scale_x_discrete(breaks=ts_df$timestamps[seq(1, nrow(ts_df), 10)])+
  ylab("Retweet Number")+
  theme_classic()+
  theme(axis.title.x=element_blank(),
    axis.text.x=element_text(size=6, angle=45, hjust=1),
        legend.position="none")

htmlwidgets::saveWidget(ggplotly(p_times), 
                        file=paste0(datadir, "/figs/timeline_", article_id, ".html"),
                        title=paste0("timeline_", article_id))

ggplotly(p_times)

```

### Distribution of tweet counts by group
```{r original, error=FALSE, warning=FALSE, fig.height=9, fig.width=18, eval=FALSE}
p_oneoff <- events %>% 
  rename(account=names, rt=retweet_screen_name) %>% 
  left_join(dmp_df2, by="account") %>% 
  dplyr::filter(is.na(retweet_screen_name)) %>%
  # mutate(rt=ifelse(is.na(rt), account, rt)) %>%
  group_by(topic) %>%
  arrange(timestamps) %>% 
  mutate(order=row_number(), n=n()) %>% 
  # dplyr::filter(n==1) %>%
  ungroup() %>%
  # group_by(topic) %>%
  # count %>%
  dplyr::filter(!is.na(topic)) %>%
  ggplot(aes(x=timestamps, y=order, group=topic, label=account))+
  # geom_line(colour="grey80")+
  geom_point(aes(colour=topic, size=wn_mean), alpha=0.5)+
  scale_colour_manual(values=cols)+
  scale_y_log10()+
  scale_x_discrete(breaks=ts_df$timestamps[seq(1, nrow(ts_df), 10)])+
  ylab("Retweet Number")+
  theme_classic()+
  theme(axis.title.x=element_blank(),
    axis.text.x=element_text(size=6, angle=45, hjust=1),
        legend.position="none")

p_balance <- events %>% 
  rename(account=names, rt=retweet_screen_name) %>% 
  left_join(dmp_df2, by="account") %>% 
  mutate(isrt=ifelse(is.na(rt), FALSE, TRUE)) %>%
  group_by(topic, isrt) %>%
  count() %>%
  ungroup() %>%
  # mutate(topic=gsub(":.*", "", topic)) %>%
  mutate(n=ifelse(isrt==TRUE, -n, n)) %>%
  # mutate(topic=as.numeric(topic)) %>%
  # mutate(topic_gp=ifelse(isrt==TRUE, -topic, topic)) %>%
  # ggplot(aes(x=factor(topic), y=n, fill=factor(topic)))+
  ggplot(aes(x=topic, y=n))+
  geom_col(aes(fill=topic))+
  geom_hline(yintercept = 0, linetype="dashed")+
  scale_fill_manual(values=cols)+
  coord_flip()+
  theme_classic()+
  theme(axis.title.x=element_blank(),
    axis.text.y=element_blank(),
    legend.position = "none")

```


# Title similarity analysis (experimental) {.tabset .tabset-fade .tabset-pills}

Not only are we interested in who is tweeting about a paper, but how they are tweeting about a paper. Is a paper's title or abstract sufficient to garner attention? Do different networks tend to editorialize or comment on a paper when they tweet about it?

To address this, we examine the cosine similarity between the text of each tweet and the text of the paper's title and abstract. Tweets that simply restate the title or snippet of the abstract will have very high cosine similarity ~1, and tweets that use very dissimilar language will have a cosine similarity ~0.

## Code

The code below calculates the cosine similarity scores (using the `sim.strings` function from the `qlcMatrix` package) between each tweet referencing the article and the title/abstract of the article itself.

```{r title_sim, error=FALSE, warning=FALSE, message=FALSE}
# title_sim <- ts_df %>% 
title_sim <- events %>% 
  # dplyr::filter(!grepl("RT @", tweets)) %>%
  mutate(tweets=gsub("http.*", "", tweets)) %>%
  mutate(tweets=gsub("\"", "", tweets)) %>%
  mutate(description = emoji_to_text(tweets)) %>%
  rename("account"="names") %>% 
  mutate(title_match_score=sim.strings(tweets, article_df$title)) %>% 
  mutate(abstract_match_score=sim.strings(tweets, abstract)) %>% 
  gather(group, value=sim_score, title_match_score:abstract_match_score) %>% #head
  left_join(lda_gammas, by="account") #%>% 
  # group_by(topic) %>% 
  # summarise(tot=mean(title_match)) 

```

## Results

### Ridgeplots

Groupwise distributions of tweet~title/abstract cosine similarity scores, displayed as ridgeplots.

```{r title_sim_ridge, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}

p_title <- title_sim %>% 
  # ggplot(aes(x=topic, y=sim_score, colour=topic, label=tweets))+
  ggplot(aes(x=sim_score, y=topic, fill=topic, label=tweets))+
  # geom_line(colour="grey80")+
  geom_density_ridges(aes(point_color = topic), scale = 4, alpha = .6, jittered_points = TRUE)+ 
  #theme_ridges() +
  # geom_boxplot()+
  # geom_jitter()+
  facet_wrap(~group)+
  # geom_point(aes(colour=topic, size=wn_mean), alpha=0.5)+
  scale_fill_manual(values=cols)+
  scale_colour_manual(values=cols, aesthetics = "point_color")+
  theme_classic()+
  theme(axis.text.y=element_blank(),
    # axis.text.x=element_text(size=6, angle=45, hjust=1),
        legend.position="none")

p_title

ggsave(paste0(datadir, "/figs/title_sim_ridges_", article_id, ".png"), 
       plot=p_title, width = 12, height=12)

```

### Boxplots

Interactive boxplots of groupwise distributions for tweet~title/abstract cosine similarity scores (based on identical data displayed in the Ridgeplots above).

```{r title_sim_box, error=FALSE, warning=FALSE, fig.height=9, fig.width=18}
p_title <- title_sim %>% 
  ggplot(aes(x=topic, y=sim_score, colour=topic, label=tweets))+
  geom_boxplot()+
  geom_jitter()+
  facet_wrap(~group)+
  scale_colour_manual(values=cols)+
  theme_classic()+
  theme(axis.text.x=element_blank(),
    # axis.text.x=element_text(size=6, angle=45, hjust=1),
        legend.position="none")


htmlwidgets::saveWidget(ggplotly(p_title), 
                        file=paste0(datadir, "/figs/title_sim_", article_id, ".html"),
                        title=paste0("title_sim_", article_id))

ggplotly(p_title) 
```
